Why Donors Donate?

### 2020-09-11 analysis/05_market_simulator.Rmd
Changed Persona Data file. Need corrected posterior draws now

# Persona Data from Market Simulator Workbook
persona_data <- readxl::read_xlsx(here('analysis', 'output', "persona_config.xlsx"))

@@

beta$levels = c("Amnesty International", "Greenpeace", "Oxfam", "Red Cross", "Environment", "Human rights", "Refugee relief", "Engages in transparency", "Engages in financial accountability","Handful of wealthy private donors", "Government Grants", "Criticized by government", "Under government crackdown")

@@

beta_persona <- as.data.frame(matrix(rep(0), nrow = 61))

@@

selectInput("ai_funding",
            label = "Select Funding source:",
            choices = c("Many small private donations",
                        "Handful of wealthy private donors",
                        "Government Grants"))

@@

selectInput("gp_funding",
            label = "Select Funding source:",
            choices = c("Many small private donations",
                        "Handful of wealthy private donors",
                        "Government Grants"))

@@

selectInput("ox_funding",
            label = "Select Funding source:",
            choices = c("Many small private donations",
                        "Handful of wealthy private donors",
                        "Government Grants"))

@@

selectInput("rc_funding",
            label = "Select Funding source:",
            choices = c("Many small private donations",
                        "Handful of wealthy private donors",
                        "Government Grants"))

>>>>

# Persona Data from Market Simulator Workbook
persona_data <- readxl::read_xlsx(here('analysis', 'output', "persona_configV06.xlsx"))

@@

beta$levels = c("Amnesty International",
                "Greenpeace", 
                "Oxfam", 
                "Red Cross",
                # Org Issue
                "Environment", 
                "Human rights",
                "Refugee relief",
                # Transparency
                "Engages in transparency",
                # Financial Accountability
                "Engages in financial accountability",
                # Funding
                "Handful of wealthy private donors", 
                "Government grants",
                # Gov Relations
                "Criticized by government",
                "Under government crackdown")

@@

beta_persona <- as.data.frame(matrix(rep(0), nrow = 111))

@@

selectInput("ai_funding",
            label = "Select Funding source:",
            choices = c("Many small private donations",
                        "Handful of wealthy private donors",
                        "Government grants"))

@@

selectInput("gp_funding",
            label = "Select Funding source:",
            choices = c("Many small private donations",
                        "Handful of wealthy private donors",
                        "Government grants"))

@@

selectInput("ox_funding",
            label = "Select Funding source:",
            choices = c("Many small private donations",
                        "Handful of wealthy private donors",
                        "Government grants"))

@@

selectInput("rc_funding",
            label = "Select Funding source:",
            choices = c("Many small private donations",
                        "Handful of wealthy private donors",
                        "Government grants"))
